Splitting it up: A split-duration package

### 2015-10-15 manuscript.tex
paper is in JSS style now

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.5in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Daniel W. Hill, Nils W. Metternich, Andreas Beger, and Michael D. Ward},
            pdftitle={Splitting it up: A split-duration package},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Splitting it up: A split-duration package}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Daniel W. Hill, Nils W. Metternich, Andreas Beger, and Michael D. Ward}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{June 8, 2015}

@@

\maketitle

\begin{abstract}
We present an implementation of split-population duration regression in the \texttt{spduration} R package and an application to data on military coups. The statistical model accounts for units that are immune to a certain outcome and not part of the duration process the researcher is primarily interested in. We provide insights that if immune units exist, we can significantly increase the predictive performance compared to standard duration model. The package includes estimation and forecasting methods for split-population Weibull and Loglogistic models.
\end{abstract}

@@

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=4in]{loglog_hazard.pdf}
\caption{Conditional hazard rate from log-logistic model.} \label{hazard}
\end{figure}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=5in]{in-sample.pdf}
\caption{{\em In-sample separation plots for Weibull and log-logistic models.}} \label{insamp}
\end{figure}

>>>>

\documentclass[article]{jss}
\usepackage[utf8]{inputenc}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\author{
Daniel W. Hill\\University of Georgia \And Nils W. Metternich\\University College London \And Andreas Beger\\who knows \And Michael D. Ward\\Duke University
}
\title{Splitting it up: the \pkg{spduration} split-population duration
regression package}
\Keywords{keywords, not capitalized, \proglang{R}}

\Abstract{
We present an implementation of split-population duration regression in
the \pkg{spduration} R package and an application to data on military
coups. The statistical model accounts for units that are immune to a
certain outcome and not part of the duration process the researcher is
primarily interested in. We provide insights that if immune units exist,
we can significantly increase the predictive performance compared to
standard duration model. The package includes estimation and forecasting
methods for split-population Weibull and Loglogistic models.
}

\Plainauthor{Daniel W. Hill, Nils W. Metternich, Andreas Beger, Michael D. Ward}
\Plaintitle{Splitting it up: the spduration split-population duration regression
package}
\Shorttitle{\pkg{spduration}: Split-population duration regression}
\Plainkeywords{keywords, not capitalized, R}

%% publication information
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
\Submitdate{}
%% \Acceptdate{2012-06-04}

\Address{
    Daniel W. Hill\\
  University of Georgia\\
  First line Second line\\
  E-mail: \href{mailto:name@company.com}{\nolinkurl{name@company.com}}\\
  URL: \url{http://rstudio.com}\\~\\
        }

\usepackage{amsmath}

@@

@@

This template demonstrates some of the basic latex you'll need to know
to create a JSS article.

\subsection{Code formatting}\label{code-formatting}

Don't use markdown, instead use the more precise latex commands:

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \proglang{Java}
\item
  \pkg{plyr}
\item
  \code{print("abc")}
\end{itemize}

\section{Introduction}\label{introduction-1}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=4in]{graphics/loglog_hazard.pdf}
\caption{Conditional hazard rate from log-logistic model.} \label{hazard}
\end{figure}

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=5in]{graphics/in-sample.pdf}
\caption{{\em In-sample separation plots for Weibull and log-logistic models.}} \label{insamp}
\end{figure}

### 2015-10-15 old-stuff/pa-letter.Rmd
paper is in JSS style now

---
author:
  - name: Daniel W. Hill
    affiliation: University of Georgia
    address: >
      First line
      Second line
    email: name@company.com
    url: http://rstudio.com
  - name: Nils W. Metternich
    affiliation: University College London
  - name: Andreas Beger
    affiliation: who knows
  - name: Michael D. Ward
    affiliation: Duke University
title:
  formatted: "Splitting it up: the \\pkg{spduration} split-population duration regression package"
  # If you use tex in the formatted title, also supply version without
  plain:     "Splitting it up: the spduration split-population duration regression package"
  # For running headers, if needed
  short:     "\\pkg{spduration}: Split-population duration regression"
abstract: >
  We present an implementation of split-population duration regression in the   \pkg{spduration} R package and an application to data on military coups. The statistical model accounts for units that are immune to a certain outcome and not part of the duration process the researcher is primarily interested in. We provide insights that if immune units exist, we can significantly increase the predictive performance compared to standard duration model. The package includes estimation and forecasting methods for split-population Weibull and Loglogistic models.
keywords:
  # at least one keyword must be supplied
  formatted: [keywords, not capitalized, "\\proglang{R}"]
  plain:     [keywords, not capitalized, R]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article
bibliography: spdur.bib
---

This template demonstrates some of the basic latex you'll need to know to create a JSS article.

## Code formatting

Don't use markdown, instead use the more precise latex commands:

* \proglang{Java}
* \pkg{plyr}
* \code{print("abc")}

@@

The last component to complete the likelihood is the choice of a distribution for the shape of the hazard rate. The \pkg{spduration} package implements two hazard rate shapes, Weibull\footnote{In the code, $f(t) = \alpha \lambda^{\alpha} t^{\alpha - 1} e^{-(\lambda t)^\alpha}$.} and log-logistic:

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=4in]{graphics/loglog_hazard.pdf}
\caption{Conditional hazard rate from log-logistic model.} \label{hazard}
\end{figure}

@@

\normalsize
The option \texttt{endSpellOnly} is set to \texttt{FALSE} so that every observation, not only those at the end of a spell, is used in the plot. By default the \texttt{plot} function will calculate the conditional hazard for each observation. The separation plot sorts observations from left to right according to the predicted probability assigned by the model (higher values to the right), and shows each event/failure as red line, with non-events shown in beige. This makes it easy to see whether the model is assigning high probabilities of failure to actual cases of failure, and low probabilities to non-failures. 
\begin{figure}[htbp!]
\centering
\includegraphics[width=5in]{graphics/in-sample.pdf}
\caption{{\em In-sample separation plots for Weibull and log-logistic models.}} \label{insamp}
\end{figure}

>>>>

---
title: "Splitting it up: A split-duration package"
author: "Daniel W. Hill, Nils W. Metternich, Andreas Beger, and Michael D. Ward"
date: "June 8, 2015"
output: 
  pdf_document:
    keep_tex: true
bibliography: spdur.bib
geometry: margin=1.5in
---

\begin{abstract}
We present an implementation of split-population duration regression in the \texttt{spduration} R package and an application to data on military coups. The statistical model accounts for units that are immune to a certain outcome and not part of the duration process the researcher is primarily interested in. We provide insights that if immune units exist, we can significantly increase the predictive performance compared to standard duration model. The package includes estimation and forecasting methods for split-population Weibull and Loglogistic models.
\end{abstract}

@@

The last component to complete the likelihood is the choice of a distribution for the shape of the hazard rate. The \texttt{spduration} package implements two hazard rate shapes, Weibull\footnote{In the code, $f(t) = \alpha \lambda^{\alpha} t^{\alpha - 1} e^{-(\lambda t)^\alpha}$.} and log-logistic:

@@

\begin{figure}[htbp!]
\centering
\includegraphics[width=4in]{loglog_hazard.pdf}
\caption{Conditional hazard rate from log-logistic model.} \label{hazard}
\end{figure}

@@

\normalsize
The option \texttt{endSpellOnly} is set to \texttt{FALSE} so that every observation, not only those at the end of a spell, is used in the plot. By default the \texttt{plot} function will calculate the conditional hazard for each observation. The separation plot sorts observations from left to right according to the predicted probability assigned by the model (higher values to the right), and shows each event/failure as red line, with non-events shown in beige. This makes it easy to see whether the model is assigning high probabilities of failure to actual cases of failure, and low probabilities to non-failures. 
\begin{figure}[htbp!]
\centering
\includegraphics[width=5in]{in-sample.pdf}
\caption{{\em In-sample separation plots for Weibull and log-logistic models.}} \label{insamp}
\end{figure}
